|

### 2024-02-28 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
model is setup. Now run simultations

if (params$replicate == TRUE) {
  box::use(
    parallel[
      detectCores
    ]
    , brms[
      brmsformula
      , cumulative
      , prior
    ]
    , rstan[stan_model]
    , ./R/helper[
      sim_all
      , discrepancy_df
      , true_positive_hist
    ]
  )
  cores <- detectCores()-1
} else {
  box::use(
   ./R/helper[
    true_positive_hist
    , discrepancy_df
   ] 
  )
}

@@

if (params$replicate == TRUE) {
  # Define model arguments
  compiled <- stan_model(
    "./STAN/move_model.stan"
    ,model_name = "moveModel"
  )
    # Run model
  modelDiscrepancies <- sim_all(
    n=c(200, 400, 600, 800)
    , num_samples = 2
    , compiled = compiled
    , cores = cores
    , model = "moveModel"
  )
    # store model
  save(
      modelDiscrepancies
      , file = "../../data/models/prr/sim/sim.RDS"
  )
} else {
  load(
    file = "../../data/models/prr/sim/sim.RDS"
  )
}
```

```{r}
#| label: fig-true-positive-rate
#| layout-nrow: 4
#| fig-width: 6
#| fig-cap: True positive rate
#| fig-subcap: 
#|  - "Red treatment"
#|  - "Blue treatment"
#|  - "Party Identification"
#|  - "Red treatment x Party Identification"
#|  - "Blue treatment x Party Identification"
#|  - "Age"
#|  - "Gender"
#|  - "White"
#|  - "Attention"
cleanNames <- c(
  "Sample size"
  , "Red treatment"
  , "Blue treatment"
  , "Partisanship"
  , "Red treatment x Partisanship"
  , "Blue treatment x Partisanship"
  , "Age"
  , "Gender"
  , "White"
  , "Attention"
)
truePositiveDF <- discrepancy_df(
  list = modelDiscrepancies
  , new_names = cleanNames
)
plotList <- lapply(
  cleanNames
  , true_positive_hist
  , df = truePositiveDF
)
plotList[[2]]
plotList[[3]]
plotList[[4]]
plotList[[5]]
plotList[[6]]
plotList[[7]]
plotList[[8]]
plotList[[9]]
```

>>>>

if (params$replicate == TRUE) {
  box::use(
    parallel[
      detectCores
    ]
    , brms[
      brmsformula
      , cumulative
      , prior
    ]
    , rstan[stan_model, rstan_options]
    , ./R/helper[
      sim_all
      , discrepancy_df
      , true_positive_hist
    ]
  )
  cores <- detectCores()-1
  rstan_options(auto_write=TRUE)
} else {
  box::use(
   ./R/helper[
    true_positive_hist
    , discrepancy_df
   ] 
  )
}

@@

if (params$replicate == TRUE) {
  # Define model arguments
  formula <- brmsformula(
    move_diff ~ RedTreatment + RepTreatment + PartyID + RedTreatment * RepTreatment * PartyID + age + gender + white + attention
  )
  compiled <- stan_model(
    "./STAN/move_post.stan"
    ,model_name = "moveModel"
  )
  family <- gaussian()
  priors <- prior(
    stats::Normal(0,1)
    ,class = b
  )
    # Run model
  modelDiscrepancies <- sim_all(
    n=c(200, 400, 600, 800)
    , num_samples = 500
    , formula = formula
    , compiled = compiled
    , family = family
    , priors = priors
    , cores = cores
    , model = "moveModel"
  )
    # store model
  save(
      modelDiscrepancies
      , file = "../../data/models/prr/sim/sim.RDS"
  )
} else {
  load(
    file = "../../data/models/prr/sim/sim.RDS"
  )
}
```

```{r}
#| label: fig-true-positive-rate
#| layout-nrow: 4
#| fig-width: 6
#| fig-cap: True positive rate
#| fig-subcap: 
#|  - "Red treatment"
#|  - "Party Identification"
#|  - "Red treatment x Party Identification"
#|  - "Age"
#|  - "Gender"
#|  - "White"
#|  - "Attention"
cleanNames <- c(
  "Sample size"
  , "Red treatment"
  , "Republican treatment"
  , "Partisanship"
  , "Red treatment x Republican treatment x Partisanship"
  , "Age"
  , "Gender"
  , "White"
  , "Attention"
)
truePositiveDF <- discrepancy_df(
  list = modelDiscrepancies
  , new_names = cleanNames
)
plotList <- lapply(
  cleanNames
  , true_positive_hist
  , df = truePositiveDF
)
plotList[[2]]
plotList[[3]]
plotList[[4]]
plotList[[5]]
plotList[[6]]
plotList[[7]]
plotList[[8]]
plotList[[9]]
```
